The evolution of the transcriptome of mammalian placentas

### 2016-11-12 manuscript/manuscript.Rnw
discuss placenta intimacy and interdigitation

\subsubsection{Degree of Intimacy}

Genes in multiple immune system-related pathways are altered in increasing degrees of intimacy

\subsubsection{Interdigitation}

>>>>

\subsubsection{Degree of Intimacy and Interdigitation}

For the degree of intimacy and interdigitation, we saw multiple genes
which were associated with different levels of interdigitiation and
intimacy (Supplemental
\cref{tab:intimacy_genes,tab:interdigitation_genes}) using an
unordered factor approach, but when we used an ordered factor
analysis, none of these genes were retained (Supplemental
\cref{tab:intimacy_genes_polr,tab:interdigitation_genes_polr}). We
suspect this is due to the small number of intermediate
interdigitation and intimacy placentas that are available. Future
analyses of additional placentas with intermediate interdigitation and
intimacy should better illuminate the pathways which are responsible
for these placental morphologies.
